Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
about successes on the memory-constrained cluster

    On the tiny cluster, \heft could produce valid assignments in $14$ experiments out of $290$ ($4.8\%$).
    The successful schedules were achieved exclusively on the tiny workflows (with only one 200-task size-increased
    workflow among them).
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm could schedule
    $94.9\%$ of workflows, thus having the smallest failure rate of $5.1\%$.

>>>>

    On the memory-constrained cluster, \heft could produce valid assignments in $14$ experiments out of $290$~($4.8\%$
    success rate).
    The successful schedules were achieved exclusively on the tiny workflows (with only two 200-task size-increased
    workflow among them).
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm
    could still schedule all of the workflows, including even the largest ones.
    As also observed on the normal cluster, \heftmm seems to be less affested by the size of the workflow when scheduling
    it.
    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.
